---
title: "Query Chinese Wordnet with CwnGraph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Query Chinese Wordnet with CwnGraph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`lexicoR` provides access to Chinese Wordnet by wrapping [`CwnGraph`](https://github.com/kylecomtw/CwnGraph/blob/master/CwnQuery.ipynb), a python package to query Chinese Wordnet.

In order to use this functionality, you need to have Python 3 installed on the computer.


## Load CwnGraph into R

The code below exposes `cwn` (python object) to the R environment:

```{r}
library(lexicoR)
load_cwn(python_path = "/usr/bin/python3", type = "python")
```

You can also use a virtual environment provided by `virtualenv` (on Linux or Mac) or `conda` (on Windows):

```r
load_cwn(python_path = "path/to/virtualenv/dir", type = "virtualenv")
```


## Query lemma and senses in Chinese Wordnet

### Query by lemma

```{r}
lemmas <- cwn$find_lemma("電腦")
lemmas
```

```{r}
lemmas[0]$senses
```

```{r}
lemmas[0]$senses[0]$relations
```

```{r}
senses <- py_to_r(lemmas[0]$senses)
for (sense in senses) {
    print(sense)
    print(sense$relations)
    cat('----\n\n')
}
```

```{r}
senses[[1]]$data()
```

### Query by sense

```{r}
cwn$find_senses(lemma="^車$")
```
```{r}
senses_related_to_wheel <- py_to_r(cwn$find_senses(definition="輪子"))
for (sense in senses_related_to_wheel) {
    print(sense)
}

```


```{r}
cwn$find_senses(examples="學步車")
```

```{r}
spend_senses <- cwn$find_senses(lemma="花費")
spend_senses[0]$facets
spend_senses[0]$all_examples()
```

